Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
including rhs.support to AR_taken

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_"),
    item_Grade = paste(`Course ID`, round(Grade,0), sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )

@@

    item_taken= paste(item, taken, sep = "_"),
    item_taken_grade= case_when(
      is.na(Grade) ~ paste(item, taken, sep = "_"),
      T            ~ paste(item, PF)
    )

     )

@@

```{r}
d_support <- d_transactions %>%
  mutate(
    grade_round = round(Grade)
  ) %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low"),
    rate.0    = mean(grade_round == 0),
    # continue with other grades
    )
```

@@

#
# Making transactions
transactions                  <- make_transaction(item = item   )
transactions_PF               <- make_transaction(item = item_PF)
transactions_HL               <- make_transaction(item = item_HL)
transactions_Grade            <- make_transaction(item = item_Grade)
transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)

transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

#
# Making sequences
sequences          <- make_sequence(item = item   )
sequences_PF       <- make_sequence(item = item_PF)
sequences_HL       <- make_sequence(item = item_HL)
sequences_Grade    <- make_sequence(item = item_Grade)

@@

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%
    mutate(
      rules = str_remove_all(rules, pattern = "[{]"),
      rules = str_remove_all(rules, pattern = "[}]"),
      `rhs.support` = confidence / lift
    ) %>%
    separate(rules, into = c("lhs", "rhs"), sep="=>") %>%
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

# Generating asocciation rules
AR_taken <- my_apriori(transactions)

@@

##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(str_detect(rhs,"fail"))
```

@@

##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(str_detect(rhs,"low"))
```

>>>>

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )

@@

    item_taken= paste(item, taken, sep = "_"),
    item_taken_grade= case_when(
      is.na(Grade) ~ paste(item, taken, sep = "_"),
      TRUE            ~ paste(item, PF)
      )
    )

@@

```{r}

n_students <- d_transactions %>%
  select(sequenceID) %>%
  n_distinct()

d_support_take <- d_transactions %>%
  distinct(
    item,
    sequenceID
    ) %>%
  group_by(
    item
    ) %>%
  summarise(
    count     = n(),
    rate.take = count / n_students
    )

d_support <- d_transactions %>%
  mutate(
    grade_round = round(Grade)
  ) %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low"),
    rate.0    = mean(grade_round <= 0),
    rate.1    = mean(grade_round <= 1),
    rate.2    = mean(grade_round <= 2),
    rate.3    = mean(grade_round <= 3),
    rate.4    = mean(grade_round <= 4),
    rate.5    = mean(grade_round <= 5),
    rate.6    = mean(grade_round <= 6),
    rate.7    = mean(grade_round <= 7),
    rate.8    = mean(grade_round <= 8),
    rate.9    = mean(grade_round <= 9),
    rate.10   = mean(grade_round <= 10)
    )

@@

#
# Making transactions
transactions                  <- make_transaction(item = item   )
transactions_PF               <- make_transaction(item = item_PF)
transactions_HL               <- make_transaction(item = item_HL)
transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)
transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

#
# Making sequences
sequences          <- make_sequence(item = item   )
sequences_PF       <- make_sequence(item = item_PF)
sequences_HL       <- make_sequence(item = item_HL)

@@

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%

    # Clean variable `rules`
    mutate(
      rules = str_remove_all(rules, pattern = "[{]"),
      rules = str_remove_all(rules, pattern = "[}]")
    ) %>%
    separate(rules, into = c("lhs", "rhs"), sep=" => ") %>%

    # Editing output
    mutate_at(
      c("support", "lhs.support", "confidence", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

# Generating asocciation rules
AR_taken <- my_apriori(transactions) %>%
  left_join(
    select(d_support_take, item, rate.take),
    by = c("rhs" = "item")
    ) %>%
  mutate(
    rhs.support = round(rate.take, 5)
    ) %>%
  select(
    - rate.take
    ) %>%
  left_join(
    select(d_support_take, item, rate.take),
    by = c("lhs" = "item")
    ) %>%
  mutate(
    lhs.support = round(rate.take, 5)
    ) %>%
  select(
    - rate.take
    ) %>%
  select(lhs, rhs, support, count, confidence, rhs.support, lift)

@@

##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(
    str_detect(rhs, "fail"),
    str_detect(lhs, "fail")
    )
```

@@

##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(
    str_detect(rhs, "low"),
    str_detect(lhs, "low")
    )
```
